Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-21 Supplemental-Material-B-Annotated-Analysis.Rmd
headings updated
data export added

### Interaction Frequency and Outgroup Attitudes

@@

### Need fulfillment, Interaction Quality, and Attitudes

@@

>>>>

### Interaction Frequency and Attitudes

@@

### Interaction Needs,Quality, and Attitudes

@@

# **Export for Methods and Results**

We also export all relevant data for the Methods and Results section, which are written in a separate RMarkdown file and is linked to the full $\LaTeX{}$ manuscript file in Overleaf.

```{r dataExport}
# collect supplementary data files
# Worker sample
dtWorkerSupp <- lapply(ls(pattern = "worker"), get)
names(dtWorkerSupp) <- ls(pattern = "worker")

# Student sample
dtStudentSupp <- lapply(ls(pattern = "student"), get)
names(dtStudentSupp) <- ls(pattern = "student")

# Medical sample
dtMedicalSupp <- lapply(ls(pattern = "medical"), get)
names(dtMedicalSupp) <- ls(pattern = "medical")

# collect and export all data files
save(list = ls(pattern = "dt"), file = "data/wrangled.RData")
```
